\documentclass{beamer}
\input{preamble}


\title{Tools and Techniques for \\ Speech and Language Processing}
\author{Lane Schwartz}
\institute[shortinst]{University of Illinois at Urbana-Champaign}

\date{Week 1 of 16}

\begin{document}

% Specify that no bibliography should be printed
\bibliographystyle{plainnat}

\frame{\titlepage}


\section{Logistics}

\frame {
\frametitle{Course web site}

\url{http://computational.linguistics.illinois.edu/lingNNN/SSSYYYY}

\ \\

\ \\

\begin{itemize}
\item Replace NNN with the course number for this course
\item Replace SSS with the current semester (fall or spring)
\item Replace YYYY with the current four-digit year
\end{itemize}

}

\frame{
\frametitle{DRES}

If a student has a disability or condition that requires special consideration, the student is expected to present the requisite letter from the University Division of Disability Resources and Educational Services (DRES) no later than the beginning of the second day of class.

}

\frame{
\frametitle{Github}

\begin{itemize}
\item Github username
\end{itemize}

}


\frame{
\frametitle{Piazza}

\begin{itemize}
\item Course Piazza site linked off course web page
\item Verify that you are enrolled in the course Piazza site
\item Ask questions via Piazza
\item Do not ask questions via email
\end{itemize}

}


\frame{
\frametitle{i$>$clicker}

\begin{itemize}
\item We will use i$>$clicker in this class.
\item You must have a physical i$>$clicker.
\item You must bring your i$>$clicker to every class session.
\item You must always have working batteries.
\item Your i$>$clicker must be registered.
\end{itemize}

}


\section{Expectations}


\frame{
\frametitle{Academic Integrity}

This course follows the University of Illinois Student Code regarding Academic Integrity. The College of Liberal Arts and Sciences also has an excellent web page on the topic. You are expected to read these resources prior to the second day of class, and to understand your responsibilities with regard to Academic Integrity.
%
All work submitted for this class must be solely your own. Violations of Academic Integrity include, but are not limited to, copying, cheating, and unapproved collaboration. 

\ \\

\textbf{Violations will not be tolerated.}

}


\section{Course Overview}

\frame{
\frametitle{Course Overview}

\begin{itemize}
\item Gain proficiency with command line tools, including git
\item Gain proficiency in shell scripting
\item Gain understanding of basic data structures
\item Gain proficiency with Python
\item Learn how to think like a programmer
\item Learn how to go from a problem statement to a solution
\end{itemize}

}

\end{document}
